Checkpoint 4

### 2020-04-30 Checkpoint 4.Rmd
Fed's models

```{r}
### For predicting one case 
new_FL <- data.frame(Day = 7 , State = FL) #Doesn't recognize state

@@

```{r}
set.seed(454)
glimpse(Finaldata)
model_data<-Finaldata%>%
  mutate(Date = as.numeric(Day))%>%
  mutate(positive_rate = positive/ totalTestResults)%>%
  select(State, ChinaVirusInterest, Day, percent_white,positive_rate)
model_data<- na.omit(model_data)

@@

```{r}
set.seed(454)
#random intercept and random slope, percent white and positive rate = positive/ total tests
#iterations might be low need to sample up if we want to make the models better
model_13 <- stan_glmer(
  ChinaVirusInterest ~ (Day | State) + percent_white +positive_rate,
  data = model_data, family = gaussian, chains = 4, iter = 3000
)
```
```{r}
head(data.frame(summary(model_13)),-2)
```

@@

ggplot(model_13_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)
```

>>>>

```{r}
### For predicting one case 
new_FL <- data.frame(Day = 7 , State = "FL") #Doesn't recognize state

@@

```{r}
glimpse(Finaldata)
model_data<-Finaldata%>%
  mutate(Date = as.numeric(Day))%>%
  mutate(positive_rate = positive/ totalTestResults,
         ChinaVirusInterest_dec = ChinaVirusInterest/100)%>%
  select(State, ChinaVirusInterest, Day, percent_white,positive_rate,ChinaVirusInterest_dec)
model_data<- na.omit(model_data)

@@

```{r}
model_data<-model_data%>%
  select(-c(ChinaVirusInterest))
set.seed(454)
#random intercept and random slope, percent white and positive rate = positive/ total tests
#iterations might be low need to sample up if we want to make the models better
model_13 <- stan_glmer(
  ChinaVirusInterest_dec ~ (Day | State) + percent_white + positive_rate,
  data = model_data, family = gaussian, chains = 4, iter = 3000
)
```
```{r}
head(data.frame(summary(model_13)),-2)
```

```{r}
pp_check(model_13)
```

@@

ggplot(model_13_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)
```
```{r}
set.seed(454)
pred_13 <- posterior_predict(
  model_13,
  newdata = model_data, transform = TRUE)

prediction_summary(y = model_data$ChinaVirusInterest,
  yrep = pred_13)
```
#Final model Fed
```{r}
### For predicting one case

new_FL <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive_rate = 0.11) #Doesn't recognize state
set.seed(454)
pred_FL <- posterior_predict(
  model_13,
  newdata = new_FL)

pred_FL <- data.frame(y_new = pred_FL[-1])

ggplot(pred_FL, aes(x=y_new))+geom_density()

summary(pred_FL)
```
